### 2017-02-12 ResearchNotes/stat_exps.tex
Adds stat 003

>>>>

\subsection{\texttt{STAT\_003} - Number of Courses per Degree}

A list of courses per degree is computed. This gives an idea of how many
courses there are in a given degree. A list of courses per degree and semester
is also given to give an idea of how the courses are distributed across the two
semesters.

Tables~\ref{tab:stat_003_res_1} and~\ref{tab:stat_003_res_2} show these results.

It should be noticeable that some degrees only have courses in one semester.
The names of the degrees are not available, only their codes. But it is
noticeable that the degree with the greater number of courses is
\texttt{B\_M\_REST\_EINF\_E}, which appears to be an Informatics Master's
Degree.

\begin{table}[h!]
    \centering

    \begin{tabular}{l r}
        Degree                             & CourseCodeMoodle \\ \hline
        \texttt{B\_M\_EHEA (478)}          & 7                \\
        \texttt{B\_M\_REST\_EINF\_E (578)} & 28               \\
        \texttt{B\_M\_REST\_TET (457)}     & 7                \\
        \texttt{B\_PD\_M\_E (580)}         & 8                \\
        \texttt{CCDND\_CPM (344)}          & 1                \\
        \texttt{FC\_CVP\_FDOC (513)}       & 2                \\
        \texttt{FC\_CVP\_UAM (514)}        & 3                \\
        \texttt{FC\_EDM (564)}             & 1                \\
        \texttt{PG\_B\_AE (438)}           & 10               \\
        \texttt{PG\_B\_EGNEG (554)}        & 10               \\
    \end{tabular}

    \caption
        [Number of Courses per Degree]
        {Number of Courses per Degree.}

    \label{tab:stat_003_res_1}
\end{table}

\begin{table}[h!]
    \centering

    \begin{tabular}{l l r}
        Degree                             & Semester       & CourseCodeMoodle \\ \hline
        \texttt{B\_M\_EHEA (478)}          & \textit{Par}   & 3                \\
                                           & \textit{Ímpar} & 4                \\
        \texttt{B\_M\_REST\_EINF\_E (578)} & \textit{Par}   & 14               \\
                                           & \textit{Ímpar} & 14               \\
        \texttt{B\_M\_REST\_TET (457)}     & \textit{Par}   & 2                \\
                                           & \textit{Ímpar} & 5                \\
        \texttt{B\_PD\_M\_E (580)}         & \textit{Par}   & 3                \\
                                           & \textit{Ímpar} & 5                \\
        \texttt{PG\_B\_EGNEG (554)}        & \textit{Par}   & 4                \\
                                           & \textit{Ímpar} & 5                \\
        \texttt{PG\_B\_AE (438)}           & \textit{Par}   & 5                \\
                                           & \textit{Ímpar} & 5                \\
        \texttt{FC\_EDM (564)}             & \textit{Par}   & 1                \\
        \texttt{CCDND\_CPM (344)}          & \textit{Ímpar} & 1                \\
        \texttt{FC\_CVP\_FDOC (513)}       & \textit{Ímpar} & 2                \\
        \texttt{FC\_CVP\_UAM (514)}        & \textit{Ímpar} & 3                \\
    \end{tabular}

    \caption
        [Number of Courses per Degree and Semester]
        {Number of Courses per Degree and Semester.}

    \label{tab:stat_003_res_2}
\end{table}
